Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-11-24 paper/cover-letter.Rnw
Just add word pollination to first sentence cover letter
Reduce margin coverletter
Formatting for Ecology

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt, a4paper]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=32em, textheight=47\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{July 5, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    Proceedings of the Royal Society B
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Proceedings B}.
The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.

>>>>

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt, a4paper]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=30em, textheight=47\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{July 5, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    Ecology
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology}.
The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same pollination community.

### 2019-11-24 paper/manuscript.Rmd
Update title
Formatting for Ecology

---
title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: bibliography.bib
csl: proceedings-of-the-royal-society-b.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
  # - \usepackage[nomarkers]{endfloat}
---

>>>>

---
title: "The trade-offs of pollinator sharing: pollination service is determined by the community context"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: bibliography.bib
csl: ecology.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 12pt
# classoption: a4paper
# geometry: 
  # - textwidth=33em
  # - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage{endfloat}
---

### 2019-11-24 paper/supp-info.Rmd
Formatting for Ecology

---
title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
subtitle: "Supplementary information"
author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
# bibliography: references.bib
csl: plos-biology.csl
documentclass: book
nocite: | 
  @Xu2003, @Nakagawa2013
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
subtitle: "Supplementary information"
author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
# bibliography: references.bib
csl: nature.csl
documentclass: book
# classoption: a4paper
nocite: | 
  @Xu2003, @Nakagawa2013
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
editor_options: 
  chunk_output_type: console
---
